---
output: github_document
bibliography: refs/add.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nCov2019_analysis

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/239410768.svg)](https://zenodo.org/badge/latestdoi/239410768)
[Rstudio ![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/JiaxiangBU/nCov2019_analysis/master?urlpath=rstudio)
[Jupyter Lab ![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/JiaxiangBU/nCov2019_analysis/master?urlpath=lab)
<!-- badges: end -->

The goal of nCov2019_analysis is to visualize the infection in Shanghai and Guizhou province using Python and R.

I borrow from the data downloading from @Isaac_Lin2020 and data manipulation from @Xu2020.

## How to use

```bash
make all
```

## Dependency

1. Python 3.7.3
1. R 3.6.0
1. 1.2.5033

## Example

See more 

1. [Shanghai infection](analysis/shanghai-ratios.md)
1. [Guihzou infection](analysis/guizhou-ratios.md)


```{r,child="analysis/shanghai-ratios.Rmd", echo=FALSE}
```

## Structure

```{r}
dir_tree(".")
```


## Citations

```{r include=FALSE}
citations <- add2pkg::add_zenodo_citation("README.Rmd")
```

```{r echo=FALSE, results='asis'}
cat(citations$Cite)
```

```{r echo=FALSE, results='asis'}
cat(paste0("```BibTex\n",citations$BibTex,"\n```"))
```

```{r echo=FALSE, results='asis'}
cat(citations$Comments)
```


`r add2pkg::add_disclaimer("Jiaxiang Li and Jian Xu and Isaac Lin")`
